Iroko: Predictive Datacenter Congestion Control

### 2017-12-12 Documents/Report/implementation.tex
Some modification to Bandwidth allocation in Implementation

\subsection{Bandwidth Allocation}
Iroko rate limits traffic at the applications level, and thus uses UDP instead of TCP to communicate with hosts. It reads a traffic matrix shared among all the hosts and sends network traffic accordingly. Iroko also manages the current allocated bandwidth per host by sending a packet which updates their current allocated bandwidth.

>>>>

\subsection{Bandwidth Allocation}
Iroko rate limits traffic at the applications level, and thus uses UDP instead of TCP to communicate with hosts. Traffic is generated using a custom load generation application we wrote which reads a traffic matrix shared among all the hosts and sends network traffic accordingly. Iroko manages the current allocated bandwidth per host by sending a controller packet which updates their current allocated bandwidth.
